---
title: "Committee Meeting Follow-ups"
author: "Windy Wang"
date: "January 31, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

library(dplyr)

ds <- readRDS(file='../data/ds.Rds') %>% 
  dplyr::mutate(logUdbpRatio = log(udbpCrRatio)) %>% 
  dplyr::select(SID, VN, fVN, Age, ACR, eGFR, UDBP,
                acr_status, eGFR_status, UDBP_status, 
                udbpCrRatio, logUdbpRatio, DM, dm_status)
  # dplyr::group_by(SID) %>% 
  # dplyr::filter(n() == 3) %>% 
  # dplyr::ungroup()

ds1 <- ds %>% 
  dplyr::filter(fVN == "Baseline")

source('../R/functions.r')
source("../R/graphs.R")
```

### UDBP Distribution

Distribution of urinary VDBP (not log adjusted)

```{r distribution}
ds %>%
  histo_plot("UDBP", 20, 'Urinary VDBP (ng/mL)',
             facet = TRUE)
```

Distribution of urinary VDBP (adjusted using natural log)
 
```{r log distribution}
ds %>%
  histo_plot("log(UDBP)", .2, 'log Urinary VDBP (ng/mL)',
             facet = TRUE)
```

### Age-ACR Associations

```{r age-ACR}
ds %>%
  scatter_plot("Age", "log(ACR)",
               "Age (Years)", "log Urine Albumin-to-Creatinine Ratio (mg/mmol)",
               facet = TRUE)
```

At baseline, there is a significant positive association.
```{r age-ACR-stats1}
ds %>%
  filter(fVN == "Baseline") %>%
  cor.test(formula = ~ Age + log(ACR), data = ., method = "spearman")
```

At 3 year, there is a significant positive association
```{r age-ACR-stats2}
ds %>%
  filter(fVN == "3Year") %>%
  cor.test(formula = ~ Age + log(ACR), data = ., method = "spearman")
```
At 6 year, there is significant positive association
```{r age-ACR-stats6}
ds %>%
  filter(fVN == "6Year") %>%
  cor.test(formula = ~ Age + log(ACR), data = ., method = "spearman")
```

### Age-eGFR Associations

```{r age-eGFR}
ds %>%
  scatter_plot("Age",
               "eGFR",
               "Age (Years)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               facet = TRUE)
```

At baseline, there is a significant positive association.
```{r age-eGFR-stats1}
ds %>%
  filter(fVN == "Baseline") %>%
  cor.test(formula = ~ Age + eGFR, data = ., method = "pearson")
```

At 3 year, there is a significant positive association
```{r age-eGFR-stats3}
ds %>%
  filter(fVN == "3Year") %>%
  cor.test(formula = ~ Age + eGFR, data = ., method = "pearson")
```
At 6 year, there is significant positive association
```{r age-eGFR-stats6}
ds %>%
  filter(fVN == "6Year") %>%
  cor.test(formula = ~ Age + eGFR, data = ., method = "pearson")
```

### UDBP Progression
```{r}
ds %>% 
  dplyr::mutate(
    UDBP1 = ifelse(VN == 1, UDBP, NA),
    UDBP3 = ifelse(VN == 3, UDBP, NA),
    UDBP6 = ifelse(VN == 6, UDBP, NA)) %>% 
  dplyr::filter(UDBP > 200) %>%
  line_plot("fVN", "UDBP", "SID",
            "Visit Number", "UDBP")
```
```{r}
ds %>% 
  box_plot("fVN", "logUdbpRatio",
           "Visit Number", "UDBP")
```

### DM and eGFR
```{r eGFR-dm}
ds %>% 
  dplyr::mutate(fDM = as.factor(DM)) %>% 
  dplyr::select(fDM, dm_status, eGFR, fVN) %>% 
  na.omit() %>% 
  line_plot("fDM", "eGFR", "fVN",
            "DM", "eGFR")
```


```{r gee}
ds %>%
  dplyr::mutate(
    udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
    ageBase = ifelse(fVN == "Baseline", Age, NA),
    fDM = relevel(as.factor(DM), "1")
    # Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  ) %>%
  dplyr::filter(!(fVN == "Baseline" &
                    acr_status == "Macroalbuminuria")) %>%
  dplyr::filter(!(fVN == "Baseline" & eGFR_status == "Moderate")) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%
  mason_gee(
    yvars = c("ACR", "eGFR"),
    xvars = "UDBP",
    covars = c("VN", "ageBase", "fDM")
  )
```

